
  
\cvsection{Projects}

\cvproject{HDFC - Mobile Banking}
\begin{itemize}
\item Enhanced HDFC BillPay System for a seamless and user-friendly bill payment experience, addressing evolving customer needs. Developing a mobile bank application for streamlined bill payments and other transactions through integration with Billdesk.
\item \textbf{Technologies}: Java, Aerospike, Redis, Java Spring Boot, GCP, GoLang, Python.\\
\end{itemize}
\smallskip
\smallskip

\cvproject{Aditya Birla Group GDNA - Birla Carbon}
\begin{itemize}
\item Computer vision for real-time CBFS flame monitoring at BIRLA CARBON, alerting process exceptions. Developed off-premise dashboards for stakeholders, providing exception summaries and trends for informed decisions.
\item \textbf{Technologies}: Python, Django, Redis, FFMPEG, Metabase, Grafana, Prometheus, Rabbit\hspace{2mm}MQ, React JS (Typescript)\\
\end{itemize}
\smallskip
\smallskip

\cvproject{
Aditya Birla Group GDNA - MILE}
\begin{itemize}
\item Implemented route optimization with ML, enabling efficient inventory and labor planning. Streamlined business operations saved the client approximately \$2 million annually through improved truckload capacity, delivery modes, and warehouse locations.
\item \textbf{Technologies}: Python, Django, ML OPS, ETL, lambda, Go, AWS, Docker, Data-bricks,  \\
\end{itemize}
\smallskip
\smallskip

\cvproject{Ultratech - U Space}
\begin{itemize}
\item Implemented seat management system for multiple organizations, optimizing workspace allocation based on health and containment zones for enhanced safety.
\item \textbf{Technologies}: Python, FastAPI, AWS, Firebase, Kafka, Linode\
\end{itemize}
\smallskip

\cvsection{Achievements}
\begin{itemize}
\item Pre finalist \textbf{\textcolor{blue}{eYantra}} Robotic Competition 2019 conducted by \textbf{IIT Bombay}.
\item Aditya Birla Group GDNA - \textbf{Best Team Award} 2021
\item \textbf{\textcolor{blue}{Google} Cloud Career Readiness Program} recipient 2021.
\item \textbf{Google Cloud} badges in DevOps, Cloud Engineering, Kubernetes, and Networking from \textbf{\textcolor{blue}{\href{https://www.qwiklabs.com/public_profiles/c11f5195-2ad0-4404-83c4-08ad982d139c}{Qwiklabs}}}
\end{itemize}
\smallskip

\cvsection{Extracurricular}
\begin{itemize}
\item \textbf{\textcolor{blue}{Co-Founder and Student Convener}} of \textbf{ Cultral Activity Developers Club}, RNSIT. The club aims at strengthening the roots of Computer Science and has more than 450 active student participants.
\end{itemize}