\documentclass[10pt,a4paper,ragged2e]{classes/altacv}
\geometry{left=1.2cm,right=10cm,marginparwidth=7.8cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

%% Document Colors

\definecolor{Black}{HTML}{1D1C1D}
\definecolor{Grey}{HTML}{2E2E2E}
\colorlet{heading}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Grey}
\colorlet{body}{Grey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}

\name{KALPAJ PISE}
\tagline{ }
\personalinfo{
  \email{\href{mailto:kalpaj12@gmail.com}{kalpaj12@gmail.com}}
  \phone{+91-8197988998}
  \location{Bengaluru, India}
  \linkedin{\href{https://linkedin.com/in/kalpaj-pise/}{kalpaj-pise}}
  \github{\href{https://github.com/kalpajpise}{kalpajpise}}
}

%% Make the header extend all the way to the right.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

%% Load Sidebar with projects.
%% Experience Section

\cvsection[sidebar]{Experience}

\cvCompany{Webknot Technologies}{Technical Lead}{07/2021 - Present\hfill Bengaluru}

\cvevent{}{HDFC Bank \textnormal{-- Contract}}{\textit{09/2022 - Present\hfill Bengaluru}}

\begin{itemize}[itemsep=5pt]
\normalsize

\item Designing distributed flows to achieve \textbf{sub-3 second} update time for modifying millions of billers using \textbf{GCS gRPC channels}, \textbf{Pub/Sub}, \textbf{Aerospike} and \textbf{Postgres Copy}.

\item Developed a full-text search engine on top of Postgres full-text, serving \textbf{120 million} users. Added a custom C extension to generate the search vectors.

\item Written \textbf{REST/gRPC} API's and \textbf{Scalable Micro Services} in \textbf{Spring Boot} and working with cross functional teams including Admin, UPI and NetBanking.

\end{itemize}

\vspace{3pt}

\cvevent{}{Aditya Birla Group - GDNA \textnormal{-- Contract}}{\textit{08/2021 - 06/2023\hfill Bengaluru}}
\begin{itemize}[itemsep=5pt]
\normalsize

\item Designed a distributed system to achieve \textbf{100fps} flame monitoring using \textbf{RabbitMQ}, \textbf{FFMPEG}, \textbf{Promethus exporter} and \textbf{time series DB} reducing process exceptions by \textbf{30\%}, and providing detailed analytics and alerts.


\item Achieved annual savings of approximately \textbf{\$2 million}, significantly enhancing operational efficiency and reducing costs.

\item Enhanced the system's performance from handling \textbf{4 concurrent users with a 40\% error rate} to managing \textbf{150 concurrent users with a 0\% error rate.}

\end{itemize}



\vspace{3pt}

\cvevent{}{Euphoric Thought Technologies \textnormal{-- Contract}}{\textit{05/2021 - 07/2021\hfill Bengaluru}}
\begin{itemize}[itemsep=5pt]
\normalsize

\item Designed a distributed system to achieve \textbf{100fps} flame monitoring using \textbf{RabbitMQ}, \textbf{FFMPEG}, \textbf{Promethus exporter} and \textbf{time series DB} reducing process exceptions by \textbf{30\%}, and providing detailed analytics and alerts.

\end{itemize}



\divider
\cvCompany{Internships}{}{}

\cvevent{}{Webknot Technologies \textnormal{-- SDE Intern}}{\textit{02/2021 - 06/2021\hfill Remote}}
\begin{itemize}[itemsep=6pt]
\normalsize

\item Spearheaded the development of Paws CRM, directing the design and implementation of its \textbf{serverless} backend using \textbf{AWS Lambda}.

\end{itemize}
\vspace{3pt}
\cvevent{}{Sahu Technologies \textnormal{-- Backend Intern}}{\textit{01/2021 - 4/2021\hfill Remote}}
\begin{itemize}[itemsep=6pt]
\normalsize
\item Migrated PHP/MySQL configuration to \textbf{Next.JS with MongoDB}. Transitioned to \textbf{AWS} instance of \textbf{RHEL} with
Amplify, resulting in a \textbf{37\%} cost reduction.
\end{itemize}

\smallskip
\begin{footnotesize}
GitHub \number \month .\number\year.version
\end{footnotesize}
\clearpage
\end{document}